External Prior Guided Internal Prior Learning for Real Noisy Image Denoising

### 2016-11-10 CVPR2017_Review_Unified.tex
add

Image denoising is a crucial and indispensable step to improve image quality in digital imaging systems. In particular, with the decrease of size of CMOS/CCD sensors, noise is more easily to be corrupted and hence denoising is becoming increasingly important for high resolution imaging. In literature of image denoising, the observed noisy image is usually modeled as $\mathbf{y}=\mathbf{x}+\mathbf{n}$, where $\mathbf{x}$ is the latent clean image and $\mathbf{n}$ is the corrupted noise. Numerous image denoising methods \cite{ksvd,lssc,nlm,bm3d,cbm3d,ncsr,pgpd,wnnm,mlp,csf,chen2015learning,foe,epll} have been proposed in the past decades, including sparse representation and dictionary learning based methods \cite{ksvd,lssc}, nonlocal self-similarity based methods \cite{nlm,bm3d,cbm3d,ncsr,pgpd}, low-rank based methods \cite{wnnm}, neural network based methods \cite{mlp}, and discriminative learning based methods \cite{csf,chen2015learning}.

@@

\begin{figure}\vspace{-0.1in}
\centering
\includegraphics[width=0.9\linewidth]{Flowchart.png}
\vspace{-0.1in}
\caption{Flowchart of the proposed external prior guided internal prior learning and real noisy image denoising framework.
}
\vspace{-0.2in}
\label{fig2}
\end{figure}

@@

%The Patch Group (PG) prior \cite{pgpd} is proposed to directly model the non-local self-similarity (NSS) property of natural images. The NSS property is commonly used in image restoration tasks \cite{nlm,bm3d,lssc,wnnm,pgpd}. The PG prior largely reduces the space of images to be modeled when compared to the patch prior \cite{epll}. In \cite{pgpd}, only the PGs of clean natural images is utilized, while the PGs of noisy input images are ignored. In this paper, we make use of PGs both from external clean images and internal given real noisy image for better denoising performance.

@@

Image priors are playing key factors in image denoising methods \cite{nlm,ksvd,epll,pgpd,Irani2013separating}. There are mainly two categories of prior learning methods: 1) External methods pre-learned priors (e.g., dictionaries) from a set of clean images, and the learned priors are used to recover the noisy images \cite{epll,pgpd}. 2) Internal methods directly learned priors from the given noisy image, and the image denoising is simultaneously done with the learning process \cite{ksvd,ple}. On one hand, the methods of \cite{epll,pgpd} demonstrated that the external priors learned from natural clean images are highly effctive and efficient for image denoising problem. On the other hand, the work of \cite{ncsr,Irani2013separating} showed that the internal priors are highly effective for removing the signal independent Gaussian noise. However, the actual noise in real noisy images are much more complex than Gaussian noise. Only using the internal information may be not enough for real image denoising problem. The methods using only the external priors are not adaptive to given real noisy images, while the methods exploiting only internal priors would be degraded by the complex noise. In this paper, we propose to combine both the external and internal priors to solve the real noisy image denoising problem.

>>>>

Image denoising is a crucial and indispensable step to improve image quality in digital imaging systems. In particular, with the decrease of size of CMOS/CCD sensors, noise is more easily to be corrupted and hence denoising is becoming increasingly important for high resolution imaging. In literature of image denoising, the observed noisy image is usually modeled as $\mathbf{y}=\mathbf{x}+\mathbf{n}$, where $\mathbf{x}$ is the latent clean image and $\mathbf{n}$ is the corrupted noise. Numerous image denoising methods \cite{ksvd,lssc,ncsr,nlm,bm3d,cbm3d,pgpd,wnnm,mlp,csf,chen2015learning,foe,epll} have been proposed in the past decades, including sparse representation and dictionary learning based methods \cite{ksvd,lssc,ncsr}, nonlocal self-similarity based methods \cite{nlm,bm3d,cbm3d,ncsr,pgpd}, low-rank based methods \cite{wnnm}, neural network based methods \cite{mlp}, and discriminative learning based methods \cite{csf,chen2015learning}.

@@

\begin{figure}\vspace{-0.1in}
\centering
\includegraphics[width=1\linewidth]{Flowchart.png}
\vspace{-0.25in}
\caption{Flowchart of the proposed external prior guided internal prior learning and real noisy image denoising framework.
}
\vspace{-0.2in}
\label{fig2}
\end{figure}

@@

@@

Image priors are playing a key role in image denoising \cite{pgpd,epll,ksvd,ple,ncsr,iraniinternal}. There are mainly two categories of prior learning methods. 1) External prior learning methods \cite{foe,pgpd,epll} learn priors (e.g., dictionaries) from a set of external clean images, and the learned priors are used to recover the latent clean image from noisy images. 2) Internal prior learning methods \cite{ksvd,ncsr,ple,iraniinternal} directly learn priors from the given noisy image, and the image denoising is often done simultaneously with the prior learning process. It has been demonstrated \cite{pgpd,epll} that the external priors learned from natural clean images are effective and efficient for image denoising problem, but they are not adaptive to the given noisy image so that some fine-scale image structures may not be well recovered. By contrast, the internal priors are adaptive to content of the given image, but the learning processing are usually slow. In addition, most of the internal prior learning methods \cite{ksvd,ncsr,ple,iraniinternal} assume AWGN noise, making the learned priors less robust for real noisy images. 
In this paper, we use external priors to guide the internal prior learning. Our method is not only much faster than the traditional internal learning methods, but also very effective to denoise real noisy images.
